%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Java \& Javascript Programmer / Devops Engineer} % Job title
    {LG Electronics.} % Organization
    {Kuala Lumpur, Malaysia} % Location
    {March. 2023 - March. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item Assisted in the development of Java applications, actively participating in code reviews and debugging sessions.
      \item Developed and maintained Java-based backend services, contributing to a 20\% increase in system efficiency.
      \item Collaborated with the frontend team to integrate JavaScript solutions, enhancing user interface responsiveness.
      \item Utilized JavaScript to create dynamic and interactive features for web and mobile applications.
      \item Implemented version control strategies, enhancing team collaboration and codebase management.
      \item Supported DevOps initiatives by configuring servers, managing databases, and automating routine tasks.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Php \& Javascript Programmer / Devops Engineer} % Job title
    {TK Education Sdn Bhd.} % Organization
    {Selangor, Malaysia} % Location
    {Nov. 2020 - May. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Configuring Linux / Apache Server
      	\item Maintaining and fixing bug of existing website ( http: //www.tutorkami.com )
      	\item Responsible for the full lifecycle (design, build, development and deployment) for the new version of http://www.tutorkami.com
      	\item Led a team of three (3) backend application developers both existing and new project.
      	\item Worked closely with the business intelligence consultants for seamless endpoint data feeds and BI endpoint presentation
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Php \& Javascript Programmer / Devops Engineer} % Job title
    {Aemulus Corporation.} % Organization
    {Penang, Malaysia} % Location
    {October. 2018 - October. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Configuring Linux / Apache Server
        \item Configuring and optimizing Mysql Server
       	\item Implemented Restful Api server for Aemulus customer
       	\item Designing and implementing microservices architecture
        \item Participated in code reviews of other developers’ work
        \item Worked on product planning along with its prototyping
        \item Collaborated with product and engineering team members to define and develop new product concepts
        \item Collaborative involvement the data engineering department to monitor, process data on daily basis
        \item Ongoing business process analysis to solve business problems
        \item Involved in development and maintenance of data pipeline automation solutions, including building new ETL logics with business intelligence applications and cloud database
        \item Create automation script for database backup and deployment code from development machine to production server
        \item Designing and implementing Docker setup for local development and production deployment
        \item Set up and managed Docker containers, running Go and PHP applications, for deployment into Kubernetes Pods.
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Php, Golang \& Javascript Programmer / Server Administrator} % Job title
    {Whizet Pvt Ltd.} % Organization
    {Penang, Malaysia} % Location
    {April. 2016 - June. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Configuring Linux / Apache Server
        \item Configuring and optimizing Mysql Server
       	\item Implemented Restful Api server for whizet.com
      	\item Working with external API (11street, Lazada, Lelong)
        \item Participated in code reviews of other developers’ work
        \item Worked on product planning along with its prototyping
        \item Collaborated with product and engineering team members to define and develop new product concepts
        \item Implemented a large part of the UI dynamic functionalities using Css, jQuery, jQuery UI, Ajax, Json, and Xml.
        \item Create automation script for database backup and deployment code from development machine to production server
        \item Enhancing existing system, convert foreground process to background process to offload time consuming task to the background
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Php \& Javascript Programmer} % Job title
    {Mobiweb Sdn Bhd.} % Organization
    {Penang, Malaysia} % Location
    {Aug. 2014 - Apr. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Managed updating of content on websites
      	\item Create custom website for company client
        \item Provided maintenance and support to business clients
        \item Fine tuning and optimizing slow mysql query to achieve optimal site response
        \item Working on fixing bug and feature expansion for company POS system ( bmo.my )
        \item Created and migrated all database objects through various development, testing, and production environments
        \item Devised solutions to expedite the procurement of required data for unique website architectures comprised of X/HTML, JavaScript, jquery, Css, and Ajax
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Php \& Javascript Programmer} % Job title
    {Resonet Sdn Bhd.} % Organization
    {Penang, Malaysia} % Location
    {Jan. 2013 - Feb. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Working in group to develop mobile9.com
        \item Work with designer to create mobile responsive site
        \item Wrote design document, test plan, and user documentation
        \item Solved problems using a combination of JavaScript, Json, and Jquery
        \item Utilized MVC principals to ensure a clean architecture and a lean code base for maximum
        \item Rewrite existing code, and add new code on top of pre-existing code.
        \item Created web sites and documentation, using HTML, to manage various projects
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Php \& Javascript Programmer / Server Administrator} % Job title
    {Dewan Perniagaan Melayu Malaysia} % Organization
    {Kajang, Malaysia} % Location
    {Dec. 2010 - Feb. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Feature expansion on existing site
        \item Develop new client project from scratch
        \item Create internal inventory system from scratch
        \item Fixing, fine tune and optimize mysql query
        \item Direct responsibility to modify, repair, update and expand existing programs and applications
      \end{cvitems}
    }


    %---------------------------------------------------------
  \cventry
    {Php \& Javascript Programmer} % Job title
    {EzyPzy Sdn Bhd} % Organization
    {Petaling Jaya, Malaysia} % Location
    {May. 2006 - July. 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item Work closely with senior to fix bug on client project
      	\item Feature expansion on existing internal system
      	\item Develop new client project from scratch using CakePhp
        \item Refactor, fixing bug on existing client project
        \item Created interactions from scratch using wireframes for the UI, and parameters from client for the functionality
      \end{cvitems}
    }

%---------------------------------------------------------

%---------------------------------------------------------
\end{cventries}
